Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*

### 2020-06-05 paper.Rmd
okay, done for friday in Seattle.

As it turns out, this decision has a dramatic impact on the AUC-ROC calculations they use to support their empirical claims. As we show below, the difference between the smoothed and original ROC AUC values is up to 0.12--a huge difference given that row-wise, the models being compared typically differ by only 0.05 or less--and this differentially impacts the models that are being compared. In fact, B&S's original results and interpretation are entirely conditional on the use of smoothed AUC-ROC. These results are shown in Tables 1 and 2.  The Goldstein, CAMEO, and Average model are everywhere superior to the theoretically informed escalation model.  Even the Quad model is generally as good as the escalation model in all implementations, and is frequently quite a bit better.

@@

The next three issues we encountered all concern information in Table 2.

>>>>

As it turns out, this decision has a dramatic impact on the AUC-ROC calculations B&S use to support their empirical claims. As we show below, the difference between the smoothed and original ROC AUC values is up to 0.12--a huge difference given that row-wise, the models being compared typically differ by only 0.05 or less--and this differentially impacts the models that are being compared. In fact, B&S's original results and interpretation are entirely conditional on the use of smoothed AUC-ROC. These results are shown in Tables 1 and 2.  The Goldstein, CAMEO, and Average model are everywhere superior to the theoretically informed escalation model.  Even the Quad model is generally as good as the escalation model in all implementations, and is frequently quite a bit better.

@@

The next three issues we encountered all concern information in B&S Table 2.
